\Large \bf Compilers Project: PTX Super-optimization

### 2018-04-30 paper/main.tex
T extends Submittable<T> //with a B at best?

@@

The program ``id'' demonstrates the identities.

>>>>

The example above is composed of two disjoint outputs, $\{d, e\}$, so the program
can process them separately to good effect.

@@

The program ``id'' demonstrates the identities: so that addition with 0, subtraction
and equivalent redundancies are eliminated.

\texttt{xor}, \texttt{and}, and \texttt{or} are supported as demonstrated by
``xor-and-or''.

``paper-example'' is the example above (so that the contents mentioned here can
be verified).
